On $R$-models

### 2019-07-03 PaperDraft.tex
updates in draft

  If $\mathcal{Q}_1$, $\mathcal{Q}_2$ are unital quantales, then a unital homomorphism if a quantale homomorphism such that $f(\varepsilon) = \varepsilon$.
\end{defin}

@@

  $\sigma(s_i) = \begin{cases}
  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a\},
  \\ \:\:\:\: \text{if $s_i \notin W \cap C \cap E$} \\
  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, s \leq \mathds{1}\},
  \\ \:\:\:\: \text{if $s_i \in W$} \\
  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \},
  \\ \:\:\:\: \text{if $s_i \in E$} \\
  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, \Box_i(a) = \{ s \in S_i \: | \: s \leq a, \forall b, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s \},
  \\ \:\:\:\: \text{if $s_i \in E$} \\
  \text{otherwise, if $s_i$ belongs to some intersection of subsets, then we combine the relevant conditions } \\
  \end{cases}$
\end{defin}

\begin{defin} Let $\mathcal{Q}$ be an unital quantale, $f : Tp \to \mathcal{Q}$ a valuation and $\sigma : I \to \Box_{\mathcal{Q}}$ a subexponential interpretation, then
  interpretation is defined inductively:

@@

@@

  \begin{enumerate}
    \item $s \in \mathcal{W}$, then $\sigma(s)$ is a unital modality.
    \item $s \in \mathcal{E}$, then $\sigma(s)$ is a central modality.
    \item $s \in \mathcal{C}$, then $\sigma(s)$ is GSI modality.
  \end{enumerate}
\end{lemma}

\begin{lemma}
  Let $s_1 \in \mathcal{W}$ and $s_1 \preceq s_2$, then $\sigma(s_2)$ is a central modality.
\end{lemma}

\begin{proof}
\end{proof}

  Let $\Sigma$ be a subexponential signature and $\sigma : \Sigma \to CN(\mathcal{Q})$ for a contravariant map
  $S : \Sigma \to Sub(\mathcal{Q})$, then:
  \begin{enumerate}
  \item For all $s_1, s_2 \in \Sigma$, if $s_1 \preceq s_2$, then $\sigma(s_2) \leq \sigma(s_1)$.
  In other words, $\sigma$ is a contravariant functor from $\Sigma$ to $Sub(\mathcal{Q})$.
  $\sigma(A) = \{ \sigma(s) \: | \: s \in A \}$ is downwardly closed, where $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$.
  \item If $s \in \mathcal{W} \cap \mathcal{C}$, then $\sigma(s)$ is a central quantic conucleus.
\end{enumerate}
\end{lemma}

@@

  \begin{enumerate}
  \item Let $s_1, s_2 \in \Sigma$ and $s_1 \leq s_2$. Then $S(s_2) \subseteq S(s_1)$.
  So, $\forall a \in \mathcal{Q}, \bigvee \{ s \in S(s_2) \: | \: s \leq a \} \leq \bigvee \{ s \in S(s_1) \: | \: s \leq a \}$. Thus, $\sigma(s_2) \leq \sigma(s_1)$.
  \item
  \item Let $s_1 \in A$ and $s_1 \preceq s_2$. By the previous part, $\sigma(s_2) \leq \sigma(s_1)$. Suppose $\sigma(s_2) \notin \sigma(A)$, then $s_2 \notin A$. But $s_2 \in A$ so far as $A$ is upwardly closed. Contradiction.
  \item Let $s \in \mathcal{W} \cap \mathcal{C}$ and $a \in \mathcal{Q}$,
  then $\sigma(s)(a) = \bigvee \{ x \in S(s) \: | \: x \leq a, x \leq \varepsilon, \text{ and } \forall b \in \mathcal{Q}, (x \cdot b) \vee (b \cdot x) \leq x \cdot b \cdot x \}$. Thus, by Lemma, $\sigma(s)(a) \in \mathcal{Z}(\mathcal{Q})$.

@@

  Let $\Sigma$ be a subexponential signature, then
  $SMALC_{\Sigma} \vdash \Gamma \rightarrow A \Rightarrow [\![\Gamma]\!] \leq [\![A]\!]$ for valuation map $f$ and for some subexponential interpretation $\sigma : \Sigma \to CN(\mathcal{Q})$.
\end{theorem}

@@

By the previous lemma, $\sigma$ is well-defined. Let us consider the case of polymodal promotion.

@@

  \begin{enumerate}
  \item $\bigvee S$ is an ideal;
  \item $A \subseteq Fm$, then $\{ B \: | \: B \rightarrow A \} = \bigvee \{ A \}$;
  \item $\bigvee \{ A \} \subseteq \bigvee \{ B \}$ iff $A \rightarrow B$;
  \item Let $\mathcal{Q} = \{ \bigvee S \: | \: S \subseteq Fm \}$ and $\bigvee \mathcal{A} \cdot \bigvee \mathcal{B} =
  \bigvee \{ A \bullet B \: | \: A \in \mathcal{A}, B \in \mathcal{B} \}$.
  Then $\langle \mathcal{Q}, \subseteq, \cdot, \bigvee{{\bf 1}}\rangle$ is a unital quantale.
  \end{enumerate}
\end{lemma}

@@

\begin{enumerate}
\item Let $!_s \in I$ and $A \mathcal{F}_{\Sigma}$, then $\Box_s (\bigvee \{ A \}) = \bigvee \{ !_s B \: | \: !_s B \rightarrow A \}$ is a quantic conucleus
\item Let $A \in \mathcal{F}_{\Sigma}$, then $\Box_s \bigvee \{ A \} = \bigvee \{ !_s A \}$, for each $s \in \mathcal{I}$
\item  Let $i, j \in I$ and $i \preceq j$, then for all $A \in \mathcal{F}_{\Sigma}$, $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
\end{enumerate}

@@

\begin{enumerate}
\item Similarly to [Yetter].
\item Let $A \in Fm$ and $s \in \mathcal{I}$.

@@

Let $\mathcal{Q}$ be a syntactic quantale defined above and $\mathcal{I} = \langle \mathcal{I}, \preceq,
\mathcal{W}, \mathcal{C}, \mathcal{E} \rangle$ be a subexponential signature.

We define a map $\Box : \mathcal{I} \to Mod_{\mathcal{Q}}$ as follows:

$\Box(i)(\bigvee \{ A \} ) = \{ !_i B \: | !_i B \rightarrow A \}$.
\end{defin}

@@

\begin{theorem}
  Let $\mathfrak{Q} = \langle \mathcal{Q}, I \rangle$ be a quantale with
  quantic conucleus. Then $\mathfrak{Q}$ is isomorphic to relational quantale on $Q$ with some conucleus.
\end{theorem}

>>>>

  If $\mathcal{Q}_1$, $\mathcal{Q}_2$ are unital quantales, then a unital homomorphism is a quantale homomorphism such that $f(\varepsilon) = \varepsilon$.
\end{defin}

@@

  $\sigma(s_i) = \begin{cases}
  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a\},
  \\ \:\:\:\: \text{if $s_i \notin W \cap C \cap E$} \\
  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a, s \leq \mathds{1}\},
  \\ \:\:\:\: \text{if $s_i \in W$} \\
  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a, s \in \mathcal{Z}(\mathcal{Q}) \},
  \\ \:\:\:\: \text{if $s_i \in E$} \\
  I_i : \mathcal{Q} \to \mathcal{Q} \text{ s.t. } \forall a \in Q, I_i(a) = \{ s \in S_i \: | \: s \leq a, \forall b, b \cdot s \vee s \cdot b \leq s \cdot b \cdot s \},
  \\ \:\:\:\: \text{if $s_i \in E$} \\
  \text{otherwise, if $s_i$ belongs to some intersection of subsets, then we combine the relevant conditions } \\
  \end{cases}$
\end{defin}

\begin{defin} Let $\mathcal{Q}$ be an unital quantale, $f : Tp \to \mathcal{Q}$ a valuation and $\sigma : I \to CN(\mathcal{Q})$ a subexponential interpretation, then interpretation is defined inductively:

@@

\begin{prop} $s \in A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$ iff $\sigma(s)$ is a unital (central or square increasing) modality.
\end{prop}

@@

  Let $\Sigma$ be a subexponential signature and $\sigma : \Sigma \to CN(\mathcal{Q})$ for a contravariant map
  $S : \Sigma \to Sub(\mathcal{Q})$, then:
  \begin{enumerate}
  \item For all $s_1, s_2 \in \Sigma$, if $s_1 \preceq s_2$, then $\sigma(s_2) \leq \sigma(s_1)$.
  In other words, $\sigma$ is a contravariant functor from $\Sigma$ to $Sub(\mathcal{Q})$.
  \item Let $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$, then $A$ is downwardly closed
  $\sigma(A) = \{ \sigma(s) \: | \: s \in A \}$ is downwardly closed, where $A = \{ \mathcal{W}, \mathcal{C}, \mathcal{E} \}$.
  \item If $s \in \mathcal{W} \cap \mathcal{C}$, then $\sigma(s)$ is a central quantic conucleus.
\end{enumerate}
\end{lemma}

@@

  \begin{enumerate}
  \item Let $s_1, s_2 \in \Sigma$ and $s_1 \leq s_2$. Then $S(s_2) \subseteq S(s_1)$.
  So, $\forall a \in \mathcal{Q}, \bigvee \{ s \in S(s_2) \: | \: s \leq a \} \leq \bigvee \{ s \in S(s_1) \: | \: s \leq a \}$. Thus, $\sigma(s_2) \leq \sigma(s_1)$.
  \item Let $\sigma(s) \in \sigma(A)$ and $\sigma(s_1) \leq \sigma(s)$, then $\sigma(s)$ is a unital (central or square increasing). By Lemma 3, $\sigma(s_1)$ is a unital (central or square increasing) too. Thus, $s_1 \in A$ and $\sigma(s_1) \in \sigma(A)$.
  \item Let $s \in \mathcal{W} \cap \mathcal{C}$ and $a \in \mathcal{Q}$,
  then $\sigma(s)(a)$. Thus, by Lemma, $\sigma(s)(a) \in \mathcal{Z}(\mathcal{Q})$.

@@

  Let $\Sigma$ be a subexponential signature, then
  $SMALC_{\Sigma} \vdash \Gamma \rightarrow A \Rightarrow [\![\Gamma]\!] \leq [\![A]\!]$.
\end{theorem}

@@

Let $\sigma$ be a subexponential interpretation. By the previous lemma, $\sigma$ is well-defined. Let us consider the case of polymodal promotion.

@@

  \begin{enumerate}
  \item $\bigvee S$ is an ideal;
  \item $A \subseteq Fm$, then $\bigvee \{ A \} = \{ B \: | \: B \rightarrow A \} = $;
  \item $\bigvee \{ A \} \subseteq \bigvee \{ B \}$ iff $A \rightarrow B$;
  \item Let $\mathcal{Q} = \{ \bigvee S \: | \: S \subseteq Fm \}$ and $\bigvee \mathcal{A} \cdot \bigvee \mathcal{B} =
  \bigvee \{ A \bullet B \: | \: A \in \mathcal{A}, B \in \mathcal{B} \}$.
  Then $\langle \mathcal{Q}, \subseteq, \cdot, \bigvee{{\bf 1}}\rangle$ is a unital quantale.
  \end{enumerate}
\end{lemma}

@@

Let $\Sigma$ be a subexponential signature.
  \begin{enumerate}
  \item Let $s \in \Sigma$, then $!_s Syn = \{ \bigvee !_s S \: | \: S \subseteq Fm \}$ is a subquantale.
  \item Let $\Sigma$ be a subexponential signature, then a map $S : \Sigma \to Sub(Syn)$ such that $S(s) = !_s Syn$ is a contravariant map
  \end{enumerate}
\end{lemma}

\begin{enumerate}
    \item One need to check that $!_s Syn = \{ \bigvee !_s S \: | \: S \subseteq Fm \}$ is closed under product and sups. Let us show that $!_s Syn$ is closed under product, so far as $!_s Syn$ is closed under sups by construction.

    Let $\bigvee !_s X, \bigvee !_s Y \in !_s Syn$. Then $\bigvee !_s X \cdot \bigvee !_s Y = \bigvee (!_s X \cdot !_s Y) \in !_s Syn$, so far as $!_s X \cdot !_s Y \subseteq Fm$.

    \item Let $s_1 \preceq s_2$ and $\bigvee !_{s_2} X \in \: !_{s_2} Syn$. Let us show that $\bigvee !_{s_2} X \in !_{s_1} Syn$.

    $\begin{array}{lll}
    & \bigvee !_{s_2} X = \{ !_{s_2} B \: | \: !_{s_2} B \to A, A \in X \} = & \\
    & \{ !_{s_2} B \: | \: !_{s_2} B \to !_{s_2} A, A \in X \} \subseteq & \\
    & \{ !_{s_2} B \: | \: !_{s_2} B \to !_{s_2} A, A \in X \} \subseteq \bigvee !_{s_1} X& \\
    \end{array}$
  \end{enumerate}
\end{proof}

Let $\Sigma$ be a subexponential signature.

\begin{enumerate}
\item Let $!_s \in \Sigma$ and $A \mathcal{F}_{\Sigma}$, then $\Box_s (\bigvee \{ A \}) = \bigvee \{ !_s B \: | \: !_s B \rightarrow A \}$ is a quantic conucleus
\item Let $A \in \mathcal{F}_{\Sigma}$, then $\Box_s \bigvee \{ A \} = \bigvee \{ !_s A \}$, for each $s \in \mathcal{I}$
\item  Let $i, j \in \Sigma$ and $i \preceq j$, then for all $A \in \mathcal{F}_{\Sigma}$, $\Box_j (\bigvee \{ A \}) \subseteq \Box_i (\bigvee \{ A \})$.
\end{enumerate}

@@

\begin{enumerate}
\item Similarly to [Yetter].
\item Let $A \in Fm$ and $s \in \Sigma$.

@@

Let $\mathcal{Q}$ be a syntactic quantale defined above and $\Sigma = \langle I, \preceq,
\mathcal{W}, \mathcal{C}, \mathcal{E} \rangle$ be a subexponential signature.

We define a map $\Box : \mathcal{I} \to Sub(Syn)$ as follows:

$\Box(s)(\bigvee \{ A \} ) = \{ !_s B \in !_s Syn \: | !_i B \rightarrow A \}$.
\end{defin}

@@

\begin{theorem}
  Let $\mathfrak{Q} = \langle \mathcal{Q}, I \rangle$ be a quantale with
  quantic conucleus. Then $\mathfrak{Q}$ is isomorphic to relational quantale on $Q$ with some conucleus operator.
\end{theorem}

### 2019-07-03 RModels.tex
representation theorem
updates in draft

@@

\begin{col}
  $ $

  Let $\mathcal{F}$ be a frame and $\mathcal{F} \restriction V$ is a generated subframe of $\mathcal{F}$.
  Then $Log(\mathcal{F}) = Log(\mathcal{F} \restriction V)$.
\end{col}

>>>>

As usual, if $V = \{ x \}$ is a singleton, then $\mathcal{F} \restriction x = \langle W \restriction x, R \cap x \rangle$ is a rooted frame (model).

@@

  By $L^{*}_{\bf S4}$ ($L_{\bf S4}$) we mean the calculus $L^{*}$ ($L$) extended with the following inference rules:

  \begin{minipage}{0.5\textwidth}
  \begin{flushleft}
    \begin{prooftree}
    \AxiomC{$\Gamma, A, \Delta \rightarrow B$}
    \RightLabel{$! \to$}
    \UnaryInfC{$\Gamma, !A, \Delta \rightarrow B$}
    \end{prooftree}
  \end{flushleft}
  \end{minipage}\hfill
  \begin{minipage}{0.5\textwidth}
  \begin{flushright}
    \begin{prooftree}
    \AxiomC{$! \Gamma \rightarrow A$}
    \RightLabel{$\to !$}
    \UnaryInfC{$! \Gamma \rightarrow ! A$}
    \end{prooftree}
  \end{flushright}
  \end{minipage}
\end{defin}

\begin{prop}
$ $

$L_{\bf S4}$ ($L^{*}_{\bf S4}$) might be equivalently defined as $L_{\bf S4}^{'} (L^{*}_{\bf S4}) = L (L^{*}) \: \oplus \: ! A \to A \: \oplus \: ! A \to !! A$ closed under monotonicity $!$-rule

\end{prop}

\begin{proof}
  \item It is clear that $L_{\bf S4} \subseteq L_{\bf S4}^{'}$. The converse inclusion is proved straightforwardly as follows:

\begin{minipage}{0.5\textwidth}
\begin{flushleft}
  \begin{prooftree}
    \AxiomC{$! A \to A$}
    \AxiomC{$\Gamma, A, \Delta \to A$}
    \RightLabel{{\bf cut}}
    \BinaryInfC{$\Gamma, ! A, \Delta \rightarrow B$}
  \end{prooftree}
\end{flushleft}
\end{minipage}\hfill
\begin{minipage}{0.5\textwidth}
\begin{flushright}
  \begin{prooftree}
    \AxiomC{$ \{ ! A_i \to ! ! A_i \}_{i = 1, \dots, n} $}
    \AxiomC{$! A_1, ! A_2, \dots, ! A_n \rightarrow B$}
    \RightLabel{{\bf mon}}
    \UnaryInfC{$!! A_1, !! A_2, \dots, !! A_n \rightarrow ! B$}
    \RightLabel{{\bf cut}}
    \BinaryInfC{$! A_1, ! A_2, \dots, ! A_n \rightarrow ! B$}
  \end{prooftree}
\end{flushright}
\end{minipage}
\end{proof}

\begin{defin}

  $ $

  A modal $R$-model $\mathfrak{M}$ is a $R$-model with additional truth condition:

  $\mathfrak{M}, \langle a, b \rangle \models ! A \Leftrightarrow \exists {R_1}_{\langle a, b \rangle} \subseteq R \text{ such that } \forall w \in R_1 \: \mathfrak{M}, w \models A$
\end{defin}

\begin{theorem}
  Let $R \subseteq W \times W$ be a (reflexive) transitive relation and $\mathcal{F} = \langle W, R \rangle$ a modal $R$-model, then $L_{\bf S4} \subseteq Log(F)$.
\end{theorem}

  We prove this theorem modulo the previous proposition for simplicity.

\begin{proof}

  \begin{enumerate}
    \item Let $\mathcal{F} \models \: ! A$, then for all $\langle a, b \rangle \in R$ and for each valuation $v$,
    $\langle \mathcal{F}, v \rangle, \langle a, b \rangle \models ! A$. Thus, $\langle \mathcal{F}, v \rangle, \langle a, b \rangle \models A$.
    \item Let $\mathcal{F} \models \: ! A$, then for all $\langle a, b \rangle \in R$, $\langle \mathcal{F}, v \rangle, \langle a, b \rangle \models ! A$,
    where $v$ is a valuation. It means that there exists $U_{\langle a, b \rangle} \subseteq R$ such that for each $u \in U$,
    $\langle \mathcal{F}, v \rangle, u \models A$.
  \end{enumerate}
\end{proof}

\begin{lemma}
  Let $\mathcal{F}_1 = \langle W_1, R_1 \rangle$ and $\mathcal{F}_2 = \langle W_2, R_2 \rangle$ be $R$-frames and $f : \mathcal{F}_1 \twoheadrightarrow \mathcal{F}_2$ a $p$-morphism. Then $p$-morphism properties also hold
\end{lemma}

  Let us show that $\langle \mathcal{F}_1, v_1 \rangle, \langle a, b \rangle \models ! A \Leftrightarrow \langle \mathcal{F}_2, v_2 \rangle, \langle f(a), f(b) \rangle \models ! A$

    $(\Rightarrow)$ Let $\langle \mathcal{F}_1, v_1 \rangle, \langle a, b \rangle \models ! A$. Then there exists a subrelation $R_1$ such that $\langle a, b \rangle$ and
    for each $p \in R_1, \langle \mathcal{F}_1, v_1 \rangle, p \models A$.
    Let us define $R_1^{'} = \{ \langle f(x), f(y) \rangle \: | \: \langle x, y \rangle \in R_1 \} \subseteq R_2$. By IH, for each $p^{'} \in R_1^{'}$,
    $\langle \mathcal{F}_1, v_1 \rangle, p \models A$. Thus, there exists a subrelation that contains $\langle f(a), f(b) \rangle$ in each pair of which $A$ is true. So, $\langle \mathcal{F}_2, v_2 \rangle, \langle f(a), f(b) \rangle \models ! A$.

    $(\Leftarrow)$ Let $\langle \mathcal{F}_2, v_2 \rangle, \langle f(a), f(b) \rangle \models ! A$. Then there exists $R_2^{'} \subseteq R_2$ such that $\langle f(a), f(b) \rangle \in R_2^{'}$ and for each $\langle c, d \rangle$, $\langle \mathcal{F}_2, v_2 \rangle, \langle c, d \rangle \models A$.

\end{proof}
